Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-08-15 talk/dls2012/paper.tex
A comment and a typo.

We run GCC with -O3 -march=native, disabling the
automatic loop vectorization. In all cases, SSE2 instructions were used for
floating point operations, except Psyco which uses x87 FPU instructions.
We also run PyPy with loop peeling optimization and without (but otherwise
identical).

@@

Loop invariant code motion has been part of early compilers in the 1960s and
1970s~\cite{allen_catalogue_1971}. The approach for achieving loop invariant
code motion is typically to perform partial redundancy elimination. The
approach was first proposed by Morel and Renvoise~\cite{morel_global_1979}. It
involves solving data flow problems usually involding bidirection data flow
equations. After improvements~\cite{chow_portable_1984,
dhamdhere_practical_1991} this approach was followed by the work of Knoop
et.al.~\cite{knoop_lazy_1992} who cleany separated the problem into a backward
and forward data flow analysis. Implementing partial redundancy elimination in
compilers that use SSA form \cite{chow_new_1997} simplified the algorithms
because no iterative data flow analysis is needed any more.

>>>>

We run GCC with -O3 -march=native, disabling the
automatic loop vectorization. In all cases, SSE2 instructions were used for
floating point operations, except Psyco which uses x87 FPU instructions.
% Psyco does not use the x87 FPU: all floating-point arithmetic is done with
% residual calls to C helpers.  These can probably be compiled with SSE2.
% But compiling CPython (and maybe Psyco) for x87 or SSE2 has probably
% no measurable effect.
We also run PyPy with loop peeling optimization and without (but otherwise
identical).

@@

Loop invariant code motion has been part of early compilers in the 1960s and
1970s~\cite{allen_catalogue_1971}. The approach for achieving loop invariant
code motion is typically to perform partial redundancy elimination. The
approach was first proposed by Morel and Renvoise~\cite{morel_global_1979}. It
involves solving data flow problems usually involding bidirection data flow
equations. After improvements~\cite{chow_portable_1984,
dhamdhere_practical_1991} this approach was followed by the work of Knoop
et.al.~\cite{knoop_lazy_1992} who cleanly separated the problem into a backward
and forward data flow analysis. Implementing partial redundancy elimination in
compilers that use SSA form \cite{chow_new_1997} simplified the algorithms
because no iterative data flow analysis is needed any more.
